A large-scale analysis of racial disparities in police stops across the United

### 2019-07-31 lib/paper_results.Rmd

We have collected and released a dataset of 
`r comma_num(pfs$counts$collected$n_stops)` traffic stops carried out by 
`r pfs$counts$collected$n_states` state patrol agencies and 
`r pfs$counts$collected$n_cities` municipal police departments.

We analyzed a unique dataset detailing 
`r comma_num(pfs$counts$analyzed$n_stops)` traffic stops carried out by 
`r pfs$counts$analyzed$n_states` state patrol agencies and 
`r pfs$counts$analyzed$n_cities` municipal police departments.

@@

```{r disparity-hit_rates-tables}
kable(disp$city$outcome$results$aggregate_hit_rates)
kable(disp$state$outcome$results$aggregate_hit_rates)
```

>>>>

We have collected and released a dataset of 
`r comma_num(pfs$counts$collected$n_stops)` traffic stops carried out by 
`r pfs$counts$collected$n_states` (`r pfs$counts$collected$n_stops_states`)
state patrol agencies and
`r pfs$counts$collected$n_cities` (`r pfs$counts$collected$n_stops_cities`)
municipal police departments.

We analyzed a unique dataset detailing 
`r comma_num(pfs$counts$analyzed$n_stops)` traffic stops carried out by 
`r pfs$counts$analyzed$n_states` (`r pfs$counts$analyzed$n_stops_states`)
state patrol agencies and
`r pfs$counts$analyzed$n_cities` (`r pfs$counts$analyzed$n_stops_cities`)
municipal police departments.

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
kable(disp$city$outcome$results$aggregate_hit_rates)
kable(disp$state$outcome$results$aggregate_hit_rates)
```
